### 2016-11-01 ms/ms.tex
updated network figure

\def\title{The temporal assembly of plant-pollinator networks
  following restoration}
\def\author{Lauren C.\ Ponisio$^{1,2}$, Marilia P. Gaiarsa$^3$, Claire
  Kremen$^1$}

@@

\def\affiliation{
  \begin{enumerate}
  \item Department of Environmental Science, Policy, and Management\\
    University of California, Berkeley\\
    130 Mulford Hall\\
    Berkeley, California, USA\\
    94720\\
  \item Department of Entomology\\
    University of California, Riverside\\
    417 Entomology Bldg.\\
    Riverside, California, USA\\
    92521\\
  \item Departamento de Ecologia\\
    Universidade de Sao Paulo\\
    S{\~a}o Paulo, SP, Brazil\\
    05508-900\\
  \end{enumerate}
}

@@

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a long-term data set comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions, contrary to what is expected through prefereantial attachment theory. High species
  and interaction turnover was ubiquitous across assembling and
  non-assembling communities, though unique interactions turned over
  at higher rates in assembling hedgerows as the networks continually
  reorganized. Nestedness of assembling networks also increased
  through time, but there was no increase in robustness to simulated
  plant extinctions. The sensitivity of networks to cascading
  perturbations, however, increased as the communities assembled, at
  least partially due to accumulating species richness. We elucidate
  some of the mechanisms underlying plant-pollinator network assembly
  and restoration, while providing further evidence that hedgerows are
  a valuable tool for promoting species conservation and ecosystem
  service? provision in agricultural areas.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/networks.pdf}
  \caption{Assembling hedgerow networks had more changing points
    (vertical red lines) than non-assembling hedgerows and weedy field
    margins (a representative sample of non-assembling sites are
    depicted here). In each network, plants and pollinators are
    represented by green and yellow circles, respectively, weighted by
    their degree. Each species has a consistent position in the
    network across years. In the assembling hedgerows, colored squares
    in the corner of each network represent the year of
    assembly. Before hedgerows are installed (when they are still
    field margins) the year of assembly is zero.}
  \label{fig:changePoints}
\end{figure}
\clearpage

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{../analysis/changePoint/plotting/communitiesSkanky2.pdf}
  \caption{The module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by community. The bottom panels
    visualize the flow of species between communities between changing
    points. }
  \label{fig:changePoints2}
\end{figure}
\clearpage

>>>>

\def\title{Major interaction reorganizations punctuate the assembly of
  pollination networks} \def\author{Lauren C.\ Ponisio$^{1,2,3}$,
  Marilia P. Gaiarsa$^4$, Claire Kremen$^1$}

@@

\def\affiliation{
  \begin{enumerate}
  \item Department of Environmental Science, Policy, and Management\\
    University of California, Berkeley\\
    130 Mulford Hall\\
    Berkeley, California, USA\\
    94720\\
  \item Berkeley Institute for Data Science (BIDS)\\
    University of California, Berkeley\\
    190 Doe Library \\
    Berkeley, California, USA\\
  \item Department of Entomology\\
    University of California, Riverside\\
    417 Entomology Bldg.\\
    Riverside, California, USA\\
    92521\\
  \item Departamento de Ecologia\\
    Universidade de Sao Paulo\\
    S{\~a}o Paulo, SP, Brazil\\
    05508-900\\
  \end{enumerate}
}

@@

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a nine-year-dataset comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions, contrary to
  what is expected through prefereantial attachment theory. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turned
  over at higher rates in assembling hedgerows as the networks
  continually reorganized. Nestedness of assembling networks also
  increased through time, but there was no increase in robustness to
  simulated plant extinctions. The sensitivity of networks to
  cascading perturbations, however, increased as the communities
  assembled, at least partially due to accumulating species
  richness. We elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation and ecosystem service? provision in
  agricultural areas.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/changePoint/plotting/networksv1.pdf}
  \caption{Assembling hedgerow networks had more changing points
    (vertical red lines) than non-assembling hedgerows and weedy field
    margins (a representative sample of non-assembling sites are
    depicted here). In each network, plants and pollinators are
    represented by green and yellow circles, respectively, weighted by
    their degree. Each species has a consistent position in the
    perimeter of the network across years. In the assembling
    hedgerows, colored squares in the corner of each network represent
    the year of assembly. Asterisks indicate the year the hegdgerow
    was planted. Before that, the sites were weedy field margins.}
  \label{fig:changePoints}
\end{figure}
\clearpage

\begin{figure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky2.pdf}
  \caption{The module membership between network changing points. Two
    representative assembling hedgerows are depicted. In the top
    panel, species are grouped by community. The bottom panels
    visualize the flow of species between communities between changing
    points. }
  \label{fig:changePoints2}
\end{figure}
\clearpage
